### 2018-01-12 submission/manuscript.tex
change the title

\section{Investigating the Microbiota and Colorectal Cancer: The
Importance of
Community}\label{investigating-the-microbiota-and-colorectal-cancer-the-importance-of-community}

>>>>

\section{Making Sense of the Noise: Leveraging Existing 16S rRNA Gene
Surveys to Identify Key Community Members in Colorectal
Cancer}\label{making-sense-of-the-noise-leveraging-existing-16s-rrna-gene-surveys-to-identify-key-community-members-in-colorectal-cancer}
